Alternate {\ttlit ACM} SIG Proceedings Paper in LaTeX Format

### 2015-08-15 sig-alternate.tex
Heat map added

\begin{figure}
    \centering
    \includegraphics[width=1\columnwidth]{rviz}
    \caption{\small Rviz screenshot with Nao, camera (Nao's feet), face marker with VFOA (gray cone) and blue marker intersecting the field of view.}
    \label{rviz}
\end{figure}

@@

\newpage
Likewise, the 3D face model is needed. The proposed head pose estimation method would work best with a 3D face model of the query subject itself. When a 3D face model of the subject is not available, as in many practical situations, a 3D face model of a subject can be used. This is an estimation of the same anthropometric points \textit{M'} (for North American Caucasians) in the 3D space \cite{farkas1994anthropometry}. Moreover, the intrinsic camera parameters are necessary to be able to compose its matrix \textit{A}. The components are expanded in equation \ref{eq:pinHole2}.

@@

\begin{figure}
    \centering
    \includegraphics[width=1\columnwidth]{realSetup}
    \caption{\small Our experimental setup: face-to-face interaction with a {\sc
            nao} robot.  The robot writes on the tactile tablet, the child then
            corrects the robot by directly overwriting its letters on the tablet
            with a stylus. An adult (either a therapist or an experimenter,
            depending on the studies), remains next to the child to guide the work. 
            A second tablet allows to choose demonstrations and the camera captures the subject's face.}
    \label{realSetup}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.7\columnwidth]{drawSetup}
    \caption{\small Graphical representation of he set-up and the possible children focuses of attention in the scene, in red.}
    \label{drawSetup}
\end{figure}

@@

Our results for a peer-to-peer work scenarios using an approach based on RGB camera are summarized in table \ref{tab:results} where the \textit{expected} is the focus of attention that given the state of the system, it is likely to attract the subject's gaze. In the same manner, the \textit{captured} is the focus of attention our approach provides and the \textit{real}, the ground truth of the subject's gaze direction based on manual annotations from two evaluators with an average reliability of $ \alpha--------\% $.

@@

\begin{figure*}
    \centering
    \includegraphics[width=2\columnwidth]{realExpected}
    \caption{\small In blue, real focus accoding to two observer assessment. In cyan, the overlap between the real and the expected focus of attentions. In yellow, the repeated pattern in turn-taking and orange is the experimenter's suggestion to switch to a difficult word}
    \label{fig:realExpected}

@@

\begin{figure*}
    \centering
    \includegraphics[width=2\columnwidth]{bitmap_zoom}
    \caption{\small At the top in blue, the real focus accoding to two observer assessment. In green, the captured focus using our aproach and in cyan, the overlap between them. At the bottom, the cosine similarity matrix between both curves with a window size of 10 seconds.}
    \label{fig:realCaptured}
\end{figure*}

@@

@@

@@

>>>>

\begin{figure}
    \centering
    \includegraphics[width=0.9\columnwidth]{rviz_camera}
    \caption{\small Rviz screenshot showing Nao, camera (Nao's feet), face detected with its field of view (gray cone) and blue marker intersecting as current VFOA.}
    \label{rviz}
\end{figure}

@@

Likewise, the 3D face model is needed. The proposed head pose estimation method would work best with a 3D face model of the query subject itself. When a 3D face model of the subject is not available, as in many practical situations, a 3D face model of a subject can be used. This is an estimation of the same anthropometric points \textit{M'} (for North American Caucasians) in the 3D space \cite{farkas1994anthropometry}. Moreover, the intrinsic camera parameters are necessary to be able to compose its matrix \textit{A}. The components are expanded in equation \ref{eq:pinHole2}.

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=1\columnwidth]{realSetup}
    \caption{\small Our experimental setup: face-to-face interaction with a {\sc
            nao} robot.  The robot writes on the tactile tablet, the child then
            corrects the robot by directly overwriting its letters on the tablet
            with a stylus. An adult (either a therapist or an experimenter,
            depending on the studies), remains next to the child to guide the work. 
            A second tablet allows to choose demonstrations and the camera captures the subject's face.}
    \label{realSetup}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.7\columnwidth]{drawSetup}
    \caption{\small Graphical representation of he set-up and the possible children focuses of attention in the scene, in red.}
    \label{drawSetup}
\end{figure}

@@

Our results for a peer-to-peer work scenarios using an approach based on RGB camera are summarized in table \ref{tab:results} where the \textit{expected} is the focus of attention that given the state of the system, it is likely to attract the subject's gaze. In the same manner, the \textit{captured} is the focus of attention our approach provides and the \textit{real}, the ground truth of the subject's gaze direction based on manual annotations from two evaluators with an average reliability of $ \alpha = .89 $.

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.8\columnwidth]{realExpected}
    \caption{\small In blue, real VFOA accoding to two observer's assessment. In cyan, the matching between the real and the obtained VFOA. In yellow, the repeated pattern in turn-taking and in orange, the experimenter's suggestion to choose a new word.}
    \label{fig:realExpected}

@@

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.8\columnwidth]{bitmap}
    \caption{\small Cosine similarity matrix between real and obtained VFOA using a 10 sec. window size computation. The correspondent numbers are shown in figure \ref{fig:realCaptured}.}
    \label{fig:bitmap}
\end{figure}

@@

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{heatmap}
    \caption{\small 2D histogram of a subject's head movements.}
    \label{heatmap}
\end{figure}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.9\columnwidth]{kmeans}
    \caption{\small K-means clustering of the VFOA.}
    \label{kmeans}
\end{figure}

@@

\begin{figure*}
    \centering
    \includegraphics[width=1.81\columnwidth]{realCaptured}
    \caption{\small Real VFOA accoding to two observer's assessment. In green, the obtained VFOA using our aproach and in cyan, the mathing between them. Finally, the correspondent numbers with figure \ref{fig:bitmap}.}
    \label{fig:realCaptured}
\end{figure*}
